rgbif: a package for working with species occurrence data in R

### 2015-10-03 manuscript.Rmd
added gitignore, manuscript edits, added refs

Users of the popular statistical and mathematical computing platform
R [@R] enjoy a wealth of readily installable comparative phylogenetic
methods and tools.

To make the capabilities of NeXML available to R users in an easy-to-use
form, and to lower the hurdles to adoption of the standard, we present
RNeXML, an R package that aims to provide easy programmatic access to
reading and writing NeXML documents, tailored for the kinds of use-cases
that will be common for users and developers of the wealth of evolutionary
analysis methods within the R ecosystem.

@@

>>>>

Biodiversity loss is one of the greatest challenges of our
time [@Pimm_2014]. Some have called this the sixth great mass
extinction [@Ceballos_2015]. Given this challenge there is a
great need for, and much research is done on, biodiversity
science. The pool of questions about biodiversity we can answer
effectively becomes much larger with more and better data.

The Global Biodiversity Information Facility (hereafter, GBIF,
http://www.gbif.org/) is the largest collection of biodiversity
records globally, currently with 580 million records, 1.6 million
taxa, 15,000 datasets from 770 publishers. In addition, large
biodiversity warehouses such as iNaturalist, VertNet, and USGS's
BISON all feed into GBIF.

Herein, we describe a library for working with GBIF data in
the R programming environment [@R]. R is an extremely widely used
language in academia, non-profits, and the private sector.
Importantly, R make it easy to do all of the steps of the
research process, including data management, data manipulation
and cleaning, statistics, and vizualization. An R client
for getting GBIF is a powerful tool for reproducible research.

# Install rgbif

@@

## Registry

```{r}
"xxx"
```

## Species

## Occurrences

### Download API

### Search API
